# figurenumbers

[![CRAN Status Badge](https://www.r-pkg.org/badges/version/figurenumbers)](https://cran.r-project.org/package=figurenumbers)
[![R-CMD-check](https://github.com/trevorld/figurenumbers/actions/workflows/R-CMD-check.yaml/badge.svg?branch=main)](https://github.com/trevorld/figurenumbers/actions)
[![Coverage Status](https://codecov.io/gh/trevorld/figurenumbers/branch/main/graph/badge.svg)](https://app.codecov.io/gh/trevorld/figurenumbers)

### Table of Contents

* [Overview](#overview)
* [Installation](#installation)
* [Examples](#examples)

## <a name="overview">Overview</a>

`{figurenumbers}` generates "connect-the-dots via math" puzzle booklets
in the style of the out-of-print *Calc-U-Draw* workbooks.  A picture is
defined as an ordered sequence of points on a 10x10 grid of the numbers
1 to 100.  Solve the first arithmetic problem and its answer is the
first point; solve the next problem and connect its point to the
previous one; and so on until the picture is revealed.

Each puzzle page is a landscape "bifold" (a landscape sheet folded once
vertically into two facing panels) with long-form arithmetic problems
on one panel and the number grid on the other.

## <a name="installation">Installation</a>

```{r install, eval = FALSE}
remotes::install_github("trevorld/figurenumbers")
```

## <a name="examples">Examples</a>

Create a printable PDF of the bundled "capital X (with slab serifs)"
puzzle.  We use `cairo_pdf()` since it more gracefully handles any
Unicode in puzzle credits than `pdf()`:

```{r example, eval = FALSE}
library("figurenumbers")
library("grid")

puzzle <- read_puzzles()$letter_x # the letter X (with slab serifs)

set.seed(42) # problem generation is random; set a seed to recreate a page
cairo_pdf("letter_x.pdf", width = 11, height = 8.5) # landscape letter
grid.draw(puzzleGrob(puzzle$segments))
invisible(dev.off())
```
