# figurenumbers

[![CRAN Status Badge](https://www.r-pkg.org/badges/version/figurenumbers)](https://cran.r-project.org/package=figurenumbers)
[![R-CMD-check](https://github.com/trevorld/figurenumbers/actions/workflows/R-CMD-check.yaml/badge.svg?branch=main)](https://github.com/trevorld/figurenumbers/actions)
[![Coverage Status](https://codecov.io/gh/trevorld/figurenumbers/branch/main/graph/badge.svg)](https://app.codecov.io/gh/trevorld/figurenumbers)

### Table of Contents

* [Overview](#overview)
* [Installation](#installation)
* [Examples](#examples)

## <a name="overview">Overview</a>

`{figurenumbers}` helps create print-and-play "connect-the-dots" puzzles where first you need to solve math problems to calculate the figure numbers and then use those numbers to draw a figure by connecting the dots in sequence with line segments in a 10x10 grid of numbers from 1 to 100.  It is inspired by the out-of-print *Calc-U-Draw* by Buki Ltd (1990) which my son liked and wanted more puzzles for but `{figurenumbers}` features new figures, randomly generated math problems, and a layout that can be used for printing out as standalone worksheets or as part of a saddle-stitched half-letter (or A5) booklet.


## <a name="installation">Installation</a>

```{r install, eval = FALSE}
remotes::install_github("trevorld/figurenumbers")
```

## <a name="examples">Examples</a>

```{r hidden, echo = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-", fig.cap = "")
```

Here we create a printable PDF of the bundled "rook" puzzle.

```{r example, eval = FALSE}
library("figurenumbers")
library("grid")
puzzle <- read_puzzles()$rook
cairo_pdf("rook_puzzle.pdf", width = 11, height = 8.5) # landscape letter
grid.draw(puzzleGrob(puzzle$segments, seed = 42, hash = puzzle$hash))
invisible(dev.off())
```
```{r example_pic, out.width = "80%", fig.width = 11, fig.height = 8.5, echo = FALSE}
library("figurenumbers")
library("grid")
puzzle <- read_puzzles()$rook
grid.draw(puzzleGrob(puzzle$segments, seed = 42, hash = puzzle$hash))
```

Here is what the "rook" figure should look like after all the math problems have been solved correctly and the corresponding line segments have been drawn in order.

```{r rook_solution, fig.width = 5, fig.height = 5, fig.alt = "Drawing of a rook figure"}
library("figurenumbers")
library("grid")
puzzle <- read_puzzles()$rook
grid.draw(numberGridGrob(puzzle$segments))
```

Here we create a two-sided printable PDF of blank number grids to hand-sketch candidate puzzle pictures on before encoding the best ones as `segments` in `inst/puzzles.yaml`.

```{r blank_grids, eval = FALSE}
library("figurenumbers")
library("grid")
cairo_pdf("blank_grids.pdf", width = 11, height = 8.5) # landscape letter
grid.draw(gridsGrob())
grid.newpage()
grid.draw(gridsGrob())
invisible(dev.off())
```
```{r blank_grids_pic, out.width = "80%", fig.width = 11, fig.height = 8.5, echo = FALSE}
library("figurenumbers")
library("grid")
grid.draw(gridsGrob())
```
